### 2019-02-21 README.Rmd
Links
Readme update

@@

1. Open and knit the `.Rmd` file found at `birthtiming/paper/paper.Rmd/` in your R libraries.
2. Clone this github repository and load the `.Rproj` file in RStudio, then knit the paper fron in `inst/paper/paper.Rmd`

In both cases, that directory will already contain a compiled version of the article current to the last commit to this repository.

>>>>

### Documents

[To access the paper directly, follow this link.](https://clanfear.github.io/birthtiming/inst/paper/paper.html)

[To access the related presentation, follow this link.](https://clanfear.github.io/birthtiming/inst/presentation/presentation.html)

@@

1. Open and knit the `.Rmd` file found at `birthtiming/paper/paper.Rmd/` in your R libraries.
2. Clone this github repository and load the `.Rproj` file in RStudio, then knit the paper fron in `inst/paper/paper.Rmd`
3. Run `birthtiming::build_birthtiming()` to knit the paper then open the paper directory with `birthtiming::open_paper_dir()` and open the file.

In all cases, that directory will already contain a compiled version of the article current to the last commit to this repository.
